---
title: "ANLY512-Q1-Q4"
format: 
  html:
    code-fold: true
editor: visual
---

In order to investigate the potential differences between car accident data from 2020 and 2021, we conducted a thorough study and analysis of the available data. Our primary goal was to explore whether there exists a discernible gap or discrepancy between the pattern of accident occurrence, such as location, time and weather, during these two years.

## **What are the top 10 states with the most accidents?**

### Top 10 States with the Most Accidents in 2020

```{r}
state10 = acc_clean20%>%group_by(State)%>%summarise(n=n())%>%arrange(-n)
state10 = state10[1:10,]
f <- ggplot(state10, aes(x = reorder(State, -n), y = n))
f =f+ geom_col(aes(fill = State),show.legend = FALSE)+theme_bw()+ # REMOVE BACKGROUND
  theme(panel.grid=element_blank())+
  theme(legend.key = element_rect(fill = "gray95"))+ #CHANGE COLOR PALETTE
  scale_colour_brewer(palette = "Pastel1")+#CHANGE COLOR PALETTE
  scale_y_continuous(labels = scales::comma)+
  labs(title="Top 10 States with the Most Accidents in 2020",
y="Number of Accidents",
x="State")
state10 = acc_clean21%>%group_by(State)%>%summarise(n=n())%>%arrange(-n)
state10 = state10[1:10,]
f1 <- ggplot(state10, aes(x = reorder(State, -n), y = n))
f1 = f1 + geom_col(aes(fill = State),show.legend = FALSE)+theme_bw()+ # REMOVE BACKGROUND
  theme(panel.grid=element_blank())+
  theme(legend.key = element_rect(fill = "gray95"))+ #CHANGE COLOR PALETTE
  scale_colour_brewer(palette = "Pastel1")+#CHANGE COLOR PALETTE
  scale_y_continuous(labels = scales::comma)+
  labs(title="Top 10 States with the Most Accidents in 2021",
y="Number of Accidents",
x="State")
grid.arrange(f, f1, ncol = 1)


```

## **What are the most common weather conditions associated with accidents?**

boxplot

```{r}
# Check the mean and median of weather conditions
summary(acc_clean$Temperature.F.)
sd(acc_clean$Temperature.F.)
summary(acc_clean$Wind_Chill.F.)
sd(acc_clean$Wind_Chill.F.)
summary(acc_clean$Humidity...)
sd(acc_clean$Humidity...)
summary(acc_clean$Pressure.in.)
sd(acc_clean$Pressure.in.)
summary(acc_clean$Visibility.mi.)
sd(acc_clean$Visibility.mi. )
summary(acc_clean$Wind_Speed.mph.)
sd(acc_clean$Wind_Speed.mph.)
summary(acc_clean$Precipitation.in.)
sd(acc_clean$Precipitation.in.)
```

## Which highway experiences the highest number of accidents?

```{r}
acc_clean$Street = as.factor(acc_clean$Street)
summary(acc_clean$Street)

```
